Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex

\sssec*{Idea of proof:} The proof will be fairly involved. To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each best lower approximation. We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and show that the set of elements we produce forms a basis.

Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction} so we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}. The first two hypotheses follow immediately from the definition of block order. Checking the third condition is quite technical but follows from certain slope conditions derived from the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.

@@

We first now show the theorem holds for $\halfcan_X$ by induction. Since $\halfcan_X$ is effective, we may induct on the degree of the log spin canonical divisor. The base case is easy: the theorem holds for $\halfcan_X' = 0$ by Example ~\ref{eg:base-1-0}. Assume it holds for $\halfcan_X' \in \di X$, with $\halfcan_X'$ effective. We will show it holds for $\halfcan_X' + P,$ verifying the inductive step. There are two cases, depending on whether $P$ is a basepoint of $\halfcan_X'$.

>>>>

\sssec*{Idea of proof:} The proof will be fairly involved. To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each positive best lower approximation of $\frac{\alpha}{\beta}$. We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and show that the set of elements we produce forms a basis.

Next, part (b) immediately follows from the conclusion of Lemma ~\ref{lem:relations_from_generators_induction}, reducing the proof to verifying the hypotheses of that lemma. 
The first two hypotheses follow immediately from the definition of block order. Checking the third condition is quite technical, but the conditions follow from certain slope conditions, given by ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.

@@

We first now show the theorem holds for $\halfcan_X$ by induction. Since $\halfcan_X$ is effective, we may induct on the degree of the log spin canonical divisor. The base case is easy: the theorem holds for $\halfcan_X' = 0$ by Example ~\ref{eg:base-1-0}. Assume it holds for $\halfcan_X' \in \di X$, with $\halfcan_X'$ effective. We will show it holds for $\halfcan_X' + P$, verifying the inductive step. There are two cases, depending on whether $P$ is a basepoint of $\halfcan_X'$.
